---
title: "Folate interactions with MICE"
author: "Josh Alampi"
date: "2022-12-15"
output: html_document
---


#load
```{r}
#clear workspace
rm(list=ls(all=TRUE))

#load packages
library(readr); library(writexl) # for read_csv(); write_xlsx()  
library(plyr) # mapvalues()
library(MASS)
library(dplyr)
library(tidyr) # for gather()
library(ggplot2)
library(ggrepel); library(ggpubr); library(scales) # extra ggplot features
library(signs) # for signs_format(), uses proper minus sign instead of hyphen
library(lmtest) # for bptest()
library(quantreg)
library(bayesQR)
select <- dplyr::select
# library(rstan)
# library(emg) # for exponentially modified gaussian model

library(mice)

data <- read.csv("//ais-fs1.sfu.ca/home2/Redirected_Profiles/jalampi/Desktop/MIREC loader 2022/clean data/2023-10-04_MIREC data.csv")
# data <- read.csv("//ais-fs1.sfu.ca/home2/Redirected_Profiles/jalampi/Desktop/MIREC loader 2022/clean data/2023-10-06_MIREC data FOR TESTING.csv")
# data <- read.csv("//ais-fs1.sfu.ca/home2/Redirected_Profiles/jalampi/Desktop/MIREC loader 2022/clean data/2024-04-02_MIREC data.csv")

data <- data %>% # restrict to only those with SRS scores
  filter(is.na(srs) == F)

```

# make functions

## Used for formatting results later
```{r}
pvalue_rounder_jama <- function(p) 
{
  require(dplyr)
  formatted_p <- case_when(
    p > 0.99 ~ "P>.99", # for P values greater than .99, report as "P>.99."
    p <= 0.99 & p > 0.05 ~ format(round(p, 2), nsmall = 2), # or P values greater than or equal to .01, report the value to the nearest hundredth
    p <= 0.05 & p >= 0.01 ~ paste0(format(round(p, 2), nsmall = 2), "*"),
    p < 0.01 & p >= 0.001 ~ paste0(format(round(p, 3), nsmall = 3), "*"), # for P values between .001 and .01, report the value to the nearest thousandth;
    p < 0.001 ~ "P<.001" # for P values less than .001, report as "P<.001"
  )
  
  return(formatted_p)
}
```

## binary or cnts z
```{r}
get_mice_res_int <- function(mira_object, alpha = 0.05,
                             round = 1, round_p = 4, name_x = "", name_z = "", 
                             levels = c(0, 1), level_names = c("","")) {
  
  # make container to store results
  table_int <- setNames(data.frame(matrix(data = NA, 
                                          nrow = 2, 
                                          ncol = 9)), #make dataframe
                        c("x_name", "z_value", "z_name", "z_level", 
                          "beta", "lb", "ub", "p_int", "ci width")) #set column names
  
  # prep z variable
  lvl1 <- levels[1] 
  lvl2 <- levels[2]
  
  name_lvl1 <- paste0(level_names[1])
  name_lvl2 <- paste0(level_names[2])
  
  # store model parameters
  res_pooled <- pool(mira_object)
  summary <- summary(res_pooled)
  
  beta_x <- summary$estimate[2]
  beta_xz <- rev(summary$estimate)[1] # selects last entry
  
  p_int <- rev(summary$p.value)[1] # selects last entry
  
  # calculate variance-covariance matrix (Using Rubin's rules)
  m <- res_pooled$m
  ubar <- Reduce("+", lapply(mira_object$analyses, vcov)) / (m)
  b <- res_pooled$pooled$b 
  vcov <- ubar + (1 + 1 / (m)) * b
  
  # store values needed for calculating intervals
  var_x <- diag(vcov)[2] 
  var_xz <- rev(diag(vcov))[1] # selects last entry
  cov_x_xz <- rev(vcov[,2])[1] # selects the last entry of the 2nd column
  
  df <- summary$df[2]
  t <- qt(1 - (alpha / 2), df) 

  # calculate beta and 95% intervals
  beta_lvl1 <- beta_x + beta_xz*lvl1 # just equals beta_x when lvl1 = 0 (default)
  beta_lvl2 <- beta_x + beta_xz*lvl2
  
  lb_lvl1 <- beta_lvl1 - ( t * sqrt(var_x + (lvl1)^2 * var_xz + 2 * lvl1 * cov_x_xz) )
  ub_lvl1 <- beta_lvl1 + ( t * sqrt(var_x + (lvl1)^2 * var_xz + 2 * lvl1 * cov_x_xz) )
  
  lb_lvl2 <- beta_lvl2 - ( t * sqrt(var_x + (lvl2)^2 * var_xz + 2 * lvl2 * cov_x_xz) )
  ub_lvl2 <- beta_lvl2 + ( t * sqrt(var_x + (lvl2)^2 * var_xz + 2 * lvl2 * cov_x_xz) )
  
  # store results
  table_int[1, 1] <- name_x
  table_int[1, 2] <- lvl1
  table_int[1, 3] <- name_z
  table_int[1, 4] <- name_lvl1
  table_int[1, 5] <- round(beta_lvl1, round) # beta coef
  table_int[1, 6] <- round(lb_lvl1, round) # lb
  table_int[1, 7] <- round(ub_lvl1, round) # ub
  table_int[1, 8] <- round(p_int, round_p) # p value for interaction
  table_int[1, 9] <- round(ub_lvl1-lb_lvl1, round) # ci width
  
  table_int[2, 1] <- name_x
  table_int[2, 2] <- lvl2
  table_int[2, 3] <- name_z
  table_int[2, 4] <- name_lvl2
  table_int[2, 5] <- round(beta_lvl2, round) # beta coef
  table_int[2, 6] <- round(lb_lvl2, round) # lb
  table_int[2, 7] <- round(ub_lvl2, round) # ub
  table_int[2, 8] <- round(p_int, round_p) # p value for interaction
  table_int[2, 9] <- round(ub_lvl2-lb_lvl2, round) # CI width
  
  return(table_int)
}
```

## 3way int: categorical 'z' with 2 levels, categorical 'w' with 3 levels
```{r}
get_mice_res_3wayint_2z3w <- function(mira_object, alpha = 0.05,
                                   round = 1, round_p = 4, name_x = "", 
                                   name_z = "", name_w = "",
                                   level_names_z = c("",""),
                                   level_names_w = c("","","") ) {
  
  # make container to store results
  table_int <- setNames(data.frame(matrix(data = NA, 
                                          nrow = 6, 
                                          ncol = 10)), #make dataframe
                        c("x_name", "z_name", "z_level", "w_name", "w_level", 
                          "beta", "lb", "ub", "p_int", "ci width")) #set column names
  
  # prep z variables
  name_z_lvl0 <- paste0(level_names_z[1])
  name_z_lvl1 <- paste0(level_names_z[2])
  
  name_w_lvl1 <- paste0(level_names_w[1])
  name_w_lvl2 <- paste0(level_names_w[2])
  name_w_lvl3 <- paste0(level_names_w[3])
  
  # start filling in table
  table_int[, 1] <- name_x
  table_int[, 2] <- name_z 
  table_int[, 4] <- name_w
  
  table_int[1:3, 3] <- name_z_lvl0
  table_int[4:6, 3] <- name_z_lvl1
  
  table_int[c(1,4), 5] <- name_w_lvl1
  table_int[c(2,5), 5] <- name_w_lvl2
  table_int[c(3,6), 5] <- name_w_lvl3
  
  # store model parameters
  
  ## prep
  res_pooled <- pool(mira_object)
  summary <- summary(res_pooled)
  
  ## calculate variance-covariance matrix (Using Rubin's rules)
  m <- res_pooled$m
  ubar <- Reduce("+", lapply(mira_object$analyses, vcov)) / (m)
  b <- res_pooled$pooled$b 
  vcov <- ubar + (1 + 1 / (m)) * b
  
  ## save order of coefficients 
  x <-         2
  x_z_1 <-     nrow(summary) - 6
  x_w_2 <-     nrow(summary) - 5
  x_w_3 <-     nrow(summary) - 4
  x_z_1_w_2 <- nrow(summary) - 1
  x_z_1_w_3 <- nrow(summary)
  
  ## save effect estimates
  estimate_x <-         summary$estimate[x]
  estimate_x_z_1 <-     summary$estimate[x_z_1]
  estimate_x_w_2 <-     summary$estimate[x_w_2]
  estimate_x_w_3 <-     summary$estimate[x_w_3]
  estimate_x_z_1_w_2 <- summary$estimate[x_z_1_w_2]
  estimate_x_z_1_w_3 <- summary$estimate[x_z_1_w_3]
  
  ## save p-values  
  p_int_x <-         summary$p.value[x]
  p_int_x_z_1 <-     summary$p.value[x_z_1]
  p_int_x_w_2 <-     summary$p.value[x_w_2]
  p_int_x_w_3 <-     summary$p.value[x_w_3]
  p_int_x_z_1_w_2 <- summary$p.value[x_z_1_w_2]
  p_int_x_z_1_w_3 <- summary$p.value[x_z_1_w_3]
  
  ## store values needed for calculating intervals
  
  ### variances
  var_x <-         diag(vcov)[x]
  var_z_1 <-       diag(vcov)[x_z_1]
  var_w_2 <-       diag(vcov)[x_w_2]
  var_w_3 <-       diag(vcov)[x_w_3]
  var_x_z_1_w_2 <- diag(vcov)[x_z_1_w_2]
  var_x_z_1_w_3 <- diag(vcov)[x_z_1_w_3]
  
  ### covariances
  cov_x_and_z_1 <-       (vcov[,x])[x_z_1]
  cov_x_and_w_2 <-       (vcov[,x])[x_w_2]
  cov_x_and_w_3 <-       (vcov[,x])[x_w_3]  
  cov_x_and_x_z_1_w_2 <- (vcov[,x])[x_z_1_w_2]
  cov_x_and_x_z_1_w_3 <- (vcov[,x])[x_z_1_w_3]
  
  cov_z_1_and_w_2 <-       (vcov[,x_z_1])[x_w_3]  
  cov_z_1_and_w_3 <-       (vcov[,x_z_1])[x_w_3]  
  cov_z_1_and_x_z_1_w_2 <- (vcov[,x_z_1])[x_z_1_w_2]  
  cov_z_1_and_x_z_1_w_3 <- (vcov[,x_z_1])[x_z_1_w_3]  
  
  cov_w_2_and_x_z_1_w_2 <- (vcov[,x_w_2])[x_z_1_w_2]  
  cov_w_3_and_x_z_1_w_3 <- (vcov[,x_w_3])[x_z_1_w_3]  
  
  ## degrees of freedom
  df_x <- summary$df[x]
  
  # don't think I need this. Use df of x, since we are estimating the effect of x on y while conditioning on Z and W. 
  # df_x_z_1 <-       summary$df[x_z_1] 
  # df_x_w_2 <-       summary$df[x_w_2]
  # df_x_w_3 <-       summary$df[x_w_3]
  # df_x_z_1_w_2 <-   summary$df[x_z_1_w_2]
  # df_x_z_1_w_3 <-   summary$df[x_z_1_w_3]
  
  # calculate effect estimates and 95% intervals
  t <- qt(1 - (alpha / 2), df_x)
  
  ## x on y when z == 0 and w == 0
  beta_x <- estimate_x
  lb_x <- beta_x - ( t * sqrt(var_x))
  ub_x <- beta_x + ( t * sqrt(var_x))
  
  table_int[1, 6] <- round(beta_x, round) # beta coef
  table_int[1, 7] <- round(lb_x, round) # lb
  table_int[1, 8] <- round(ub_x, round) # ub
  table_int[1, 9] <- NA # p-int.
  
  ## x on y when z == 0 and w == 2
  beta_x_w_2 <- estimate_x + estimate_x_w_2
  lb_x_w_2 <- beta_x_w_2 - ( t * sqrt(var_x + var_w_2 + 2*cov_x_and_w_2) )
  ub_x_w_2 <- beta_x_w_2 + ( t * sqrt(var_x + var_w_2 + 2*cov_x_and_w_2) )
    
  table_int[2, 6] <- round(beta_x_w_2, round) # beta coef
  table_int[2, 7] <- round(lb_x_w_2, round) # lb
  table_int[2, 8] <- round(ub_x_w_2, round) # ub
  table_int[2, 9] <- round(p_int_x_w_2, round_p) # p-int.
  
  ## x on y when z == 0 and w == 3
  beta_x_w_3 <- estimate_x + estimate_x_w_3
  lb_x_w_3 <- beta_x_w_3 - ( t * sqrt(var_x + var_w_3 + 2*cov_x_and_w_3) )
  ub_x_w_3 <- beta_x_w_3 + ( t * sqrt(var_x + var_w_3 + 2*cov_x_and_w_3) )
  
  table_int[3, 6] <- round(beta_x_w_3, round) # beta coef
  table_int[3, 7] <- round(lb_x_w_3, round) # lb
  table_int[3, 8] <- round(ub_x_w_3, round) # ub
  table_int[3, 9] <- round(p_int_x_w_3, round_p) # p-int.
  
  ## x on y when z == 1 and w == 0 
  beta_x_z_1 <- estimate_x + estimate_x_z_1
  lb_x_z_1 <- beta_x_z_1 - ( t * sqrt(var_x + var_z_1 + 2*cov_x_and_z_1) )
  ub_x_z_1 <- beta_x_z_1 + ( t * sqrt(var_x + var_z_1 + 2*cov_x_and_z_1) )
  
  table_int[4, 6] <- round(beta_x_z_1, round) # beta coef
  table_int[4, 7] <- round(lb_x_z_1, round) # lb
  table_int[4, 8] <- round(ub_x_z_1, round) # ub
  table_int[4, 9] <- round(p_int_x_z_1, round_p) # p-int.
  
  ## x on y when z == 1 and w == 2
  beta_x_z_1_and_w_2 <- estimate_x + estimate_x_z_1 + estimate_x_w_2 + estimate_x_z_1_w_2
  lb_x_z_1_and_w_2 <- beta_x_z_1_and_w_2 - ( t * sqrt(
    var_x + var_z_1 + var_w_2 + var_x_z_1_w_2 +
      2*cov_x_and_w_2 + 2*cov_x_and_z_1 + 2*cov_x_and_x_z_1_w_2 +
      2*cov_z_1_and_w_2 + 2*cov_z_1_and_x_z_1_w_2 + 2*cov_w_2_and_x_z_1_w_2) )

  ub_x_z_1_and_w_2 <- beta_x_z_1_and_w_2 + ( t * sqrt(
    var_x + var_z_1 + var_w_2 + var_x_z_1_w_2 +
      2*cov_x_and_w_2 + 2*cov_x_and_z_1 + 2*cov_x_and_x_z_1_w_2 +
      2*cov_z_1_and_w_2 + 2*cov_z_1_and_x_z_1_w_2 + 2*cov_w_2_and_x_z_1_w_2) )

  table_int[5, 6] <- round(beta_x_z_1_and_w_2, round) # beta coef
  table_int[5, 7] <- round(lb_x_z_1_and_w_2, round) # lb
  table_int[5, 8] <- round(ub_x_z_1_and_w_2, round) # ub
  table_int[5, 9] <- round(p_int_x_z_1_w_2, round_p) # p-int.

  ## x on y when z == 1 and w == 3
  beta_x_z_1_and_w_3 <- estimate_x + estimate_x_z_1 + estimate_x_w_3 + estimate_x_z_1_w_3
  lb_x_z_1_and_w_3 <- beta_x_z_1_and_w_3 - ( t * sqrt(
    var_x + var_z_1 + var_w_3 + var_x_z_1_w_3 +
      2*cov_x_and_w_3 + 2*cov_x_and_z_1 + 2*cov_x_and_x_z_1_w_3 +
      2*cov_z_1_and_w_3 + 2*cov_z_1_and_x_z_1_w_3 + 2*cov_w_3_and_x_z_1_w_3) )

  ub_x_z_1_and_w_3 <- beta_x_z_1_and_w_3 + ( t * sqrt(
    var_x + var_z_1 + var_w_3 + var_x_z_1_w_3 +
      2*cov_x_and_w_3 + 2*cov_x_and_z_1 + 2*cov_x_and_x_z_1_w_3 +
      2*cov_z_1_and_w_3 + 2*cov_z_1_and_x_z_1_w_3 + 2*cov_w_3_and_x_z_1_w_3) )

  table_int[6, 6] <- round(beta_x_z_1_and_w_3, round) # beta coef
  table_int[6, 7] <- round(lb_x_z_1_and_w_3, round) # lb
  table_int[6, 8] <- round(ub_x_z_1_and_w_3, round) # ub
  table_int[6, 9] <- round(p_int_x_z_1_w_3, round_p) # p-int.

  
  for(i in 1:6){ # find CI width. Not reported, but interesting to see how wide the CIs are. 
    table_int[i, 10] <- table_int[i, 8] - table_int[i, 7]
  }
  
  return(table_int)
}


```

## 3way int: categorical 'Z' with 2 levels, categorical 'w' with 2 levels
```{r}


get_mice_res_3wayint_2z2w <- function(mira_object, alpha = 0.05,
                                  round = 1, round_p = 4, name_x = "", 
                                  name_z = "", name_w = "",
                                  level_names_z = c("",""),
                                  level_names_w = c("","") ) {
  
  # make container to store results
  table_int <- setNames(data.frame(matrix(data = NA, 
                                          nrow = 4, 
                                          ncol = 10)), #make dataframe
                        c("x_name", "z_name", "z_level", "w_name", "w_level", 
                          "beta", "lb", "ub", "p_int", "ci width")) #set column names
  
  # prep z variables
  name_z_lvl0 <- paste0(level_names_z[1])
  name_z_lvl1 <- paste0(level_names_z[2])
  
  name_w_lvl0 <- paste0(level_names_w[1])
  name_w_lvl1 <- paste0(level_names_w[2])

  
  # start filling in table
  table_int[, 1] <- name_x
  table_int[, 2] <- name_z 
  table_int[, 4] <- name_w
  
  table_int[1:2, 3] <- name_z_lvl0
  table_int[3:4, 3] <- name_z_lvl1
  
  table_int[c(1,3), 5] <- name_w_lvl0
  table_int[c(2,4), 5] <- name_w_lvl1

  # store model parameters
  
  ## prep
  res_pooled <- pool(mira_object)
  summary <- summary(res_pooled)
  
  ## calculate variance-covariance matrix (Using Rubin's rules)
  m <- res_pooled$m
  ubar <- Reduce("+", lapply(mira_object$analyses, vcov)) / (m)
  b <- res_pooled$pooled$b 
  vcov <- ubar + (1 + 1 / (m)) * b
  
  ## save order of coefficients 
  x <-         2
  x_z_1 <-     nrow(summary) - 3
  x_w_1 <-     nrow(summary) - 2
  x_z_1_w_1 <- nrow(summary) 
  
  ## save effect estimates
  estimate_x <-         summary$estimate[x]
  estimate_x_z_1 <-     summary$estimate[x_z_1]
  estimate_x_w_1 <-     summary$estimate[x_w_1]
  estimate_x_z_1_w_1 <- summary$estimate[x_z_1_w_1]
  
  ## save p-values  
  p_int_x <-         summary$p.value[x]
  p_int_x_z_1 <-     summary$p.value[x_z_1]
  p_int_x_w_1 <-     summary$p.value[x_w_1]
  p_int_x_z_1_w_1 <- summary$p.value[x_z_1_w_1]
  
  ## store values needed for calculating intervals
  
  ### variances
  var_x <-           diag(vcov)[x]
  var_x_z_1 <-       diag(vcov)[x_z_1]
  var_x_w_1 <-       diag(vcov)[x_w_1]
  var_x_z_1_w_1 <-   diag(vcov)[x_z_1_w_1]
  
  ### covariances
  cov_x_and_x_z_1 <-         (vcov[,x])[x_z_1]
  cov_x_and_x_w_1 <-         (vcov[,x])[x_w_1]
  cov_x_and_x_z_1_w_1 <-     (vcov[,x])[x_z_1_w_1]
  
  cov_x_z_1_and_x_w_1 <-     (vcov[,x_z_1])[x_w_1]  
  cov_x_z_1_and_x_z_1_w_1 <- (vcov[,x_z_1])[x_z_1_w_1]  
  
  cov_x_w_1_and_x_z_1_w_1 <- (vcov[,x_w_1])[x_z_1_w_1]
  
  ## degrees of freedom
  df_x <- summary$df[x]
  
  # calculate effect estimates and 95% intervals
  t <- qt(1 - (alpha / 2), df_x)
  
  ## x on y when z == 0 and w == 0
  beta_x <- estimate_x
  lb_x <- beta_x - ( t * sqrt(var_x))
  ub_x <- beta_x + ( t * sqrt(var_x))
  
  table_int[1, 6] <- round(beta_x, round) # beta coef
  table_int[1, 7] <- round(lb_x, round) # lb
  table_int[1, 8] <- round(ub_x, round) # ub
  table_int[1, 9] <- NA # p-int.
  
  
  ## x on y when z == 0 and w == 1
  beta_x_w_1 <- estimate_x + estimate_x_w_1
  lb_x_w_1 <- beta_x_w_1 - ( t * sqrt(var_x + var_x_w_1 + 2*cov_x_and_x_w_1) )
  ub_x_w_1 <- beta_x_w_1 + ( t * sqrt(var_x + var_x_w_1 + 2*cov_x_and_x_w_1) )
  
  table_int[2, 6] <- round(beta_x_w_1, round) # beta coef
  table_int[2, 7] <- round(lb_x_w_1, round) # lb
  table_int[2, 8] <- round(ub_x_w_1, round) # ub
  table_int[2, 9] <- round(p_int_x_w_1, round_p) # p-int.
  
  
  ## x on y when z == 1 and w == 0 
  beta_x_z_1 <- estimate_x + estimate_x_z_1
  lb_x_z_1 <- beta_x_z_1 - ( t * sqrt(var_x + var_x_z_1 + 2*cov_x_and_x_z_1) )
  ub_x_z_1 <- beta_x_z_1 + ( t * sqrt(var_x + var_x_z_1 + 2*cov_x_and_x_z_1) )
  
  table_int[3, 6] <- round(beta_x_z_1, round) # beta coef
  table_int[3, 7] <- round(lb_x_z_1, round) # lb
  table_int[3, 8] <- round(ub_x_z_1, round) # ub
  table_int[3, 9] <- round(p_int_x_z_1, round_p) # p-int.
  
  
  ## x on y when z == 1 and w == 1
  beta_x_z_1_and_x_w_1 <- estimate_x + estimate_x_z_1 + estimate_x_w_1 + estimate_x_z_1_w_1
  lb_x_z_1_and_x_w_1 <- beta_x_z_1_and_x_w_1 - ( t * sqrt(
    var_x + var_x_z_1 + var_x_w_1 + var_x_z_1_w_1 +
      2*cov_x_and_x_w_1 + 2*cov_x_and_x_z_1 + 2*cov_x_and_x_z_1_w_1 +
      2*cov_x_z_1_and_x_w_1 + 2*cov_x_z_1_and_x_z_1_w_1 + 2*cov_x_w_1_and_x_z_1_w_1) )
  
  ub_x_z_1_and_x_w_1 <- beta_x_z_1_and_x_w_1 + ( t * sqrt(
    var_x + var_x_z_1 + var_x_w_1 + var_x_z_1_w_1 +
      2*cov_x_and_x_w_1 + 2*cov_x_and_x_z_1 + 2*cov_x_and_x_z_1_w_1 +
      2*cov_x_z_1_and_x_w_1 + 2*cov_x_z_1_and_x_z_1_w_1 + 2*cov_x_w_1_and_x_z_1_w_1) )
  
  table_int[4, 6] <- round(beta_x_z_1_and_x_w_1, round) # beta coef
  table_int[4, 7] <- round(lb_x_z_1_and_x_w_1, round) # lb
  table_int[4, 8] <- round(ub_x_z_1_and_x_w_1, round) # ub
  table_int[4, 9] <- round(p_int_x_z_1_w_1, round_p) # p-int.
  
  
  
  for(i in 1:4){ # find CI width. Not reported, but interesting to see how wide the CIs are. 
    table_int[i, 10] <- table_int[i, 8] - table_int[i, 7]
  }
  
  return(table_int)
}
```


# clean data

## Define reference levels
The level that is the most common will be the reference level
```{r}
data$fol.intake3 <- factor(data$fol.intake3, levels = c(2, 1, 3))

data$city10 <- factor(data$city10, levels = c(9,1,2,3,4,5,6,7,8,10)) # Montreal is Reference
data$edu4 <- factor(data$edu4, levels = c(3,1,2,4)) # undergrad is reference
data$income4 <- factor(data$income4, levels= c(4,1,2,3)) # >100K is reference
# data$mom.age3 <- factor(data$mom.age3, levels= c(2,1,3)) # 30-39 years old is reference # CUT
data$parity3 <- factor(data$parity3, levels= c(1,2,3)) #nulliparous is reference

data <- mutate(data, year.enroll4 = year.enroll4 - 2007)
data$year.enroll4 <- factor(data$year.enroll4, levels = c(3, 1, 2, 4)) # 2010 is reference

```

```{r}
data$mthfr677_cat <- factor(data$mthfr677_cat, levels = c("C|C", "C|T", "T|T"))
```

## Make new version of mthfr677_cat
```{r}
data <- data %>%
  mutate(mthfr677_dom = ifelse(mthfr677_cat == "C|T" | mthfr677_cat == "T|T",
                               1, 0)) %>%
  mutate(mthfr677_rec = ifelse(mthfr677_cat == "T|T",
                               1, 0))
```


## make mean = zero for the continuous confounding variables
```{r}
data <- mutate(data, home.score = home.score - mean(home.score, na.rm = T))
data <- mutate(data, srs.age = srs.age - mean(srs.age, na.rm = T))
data <- mutate(data, mom.age = mom.age - mean(mom.age))
```


## Make new folate variables
10th and 80th percentiles will be used for the main analysis
20th percentile will be used for three way interaction analysis
```{r}
# define the cutoffs for the plasma-folate variable
pl_fol_10.t1 <- quantile(data$tot_fol.t1, 0.1, na.rm = T)
pl_fol_80.t1 <- quantile(data$tot_fol.t1, 0.8, na.rm = T)

pl_fol_20.t1 <- quantile(data$tot_fol.t1, 0.2, na.rm = T)

# make new categorical variable
data <- data %>% 
  mutate(pl_fol3.t1 = case_when(tot_fol.t1 < pl_fol_10.t1 ~ 1,
                                tot_fol.t1 >= pl_fol_10.t1 & tot_fol.t1 < pl_fol_80.t1 ~2,
                                tot_fol.t1 >= pl_fol_80.t1 ~ 3) ) %>% 
  mutate(pl_fol2.t1 = ifelse(tot_fol.t1 >= pl_fol_20.t1, "high", "low"))

data$pl_fol3.t1 <- factor(data$pl_fol3.t1, levels = c(2, 1, 3))


# define the cutoffs for the plasma-folate variable
pl_fol_10.t3 <- quantile(data$tot_fol.t3, 0.1, na.rm = T)
pl_fol_80.t3 <- quantile(data$tot_fol.t3, 0.8, na.rm = T)

pl_fol_20.t3 <- quantile(data$tot_fol.t3, 0.2, na.rm = T)

# make new categorical variable
data <- data %>% 
  mutate(pl_fol3.t3 = case_when(tot_fol.t3 < pl_fol_10.t3 ~ 1,
                                tot_fol.t3 >= pl_fol_10.t3 & tot_fol.t3 < pl_fol_80.t3 ~2,
                                tot_fol.t3 >= pl_fol_80.t3 ~ 3) ) %>% 
  mutate(pl_fol2.t3 = ifelse(tot_fol.t3 >= pl_fol_20.t3, "high", "low")) 

data$pl_fol3.t3 <- factor(data$pl_fol3.t3, levels = c(2, 1, 3))

```

## remove variables that MICE should ignore
The following auxiliary variables will be used:
alc2 (consumed alcohol during pregnancy or not), mom.birthplace5, prepreg.bmi, 3 metals (As, Cd, Hg) measured at first and third trimesters, and the folate vitamers (umfa, 5-mTHF, sum of non-methylated folate) measured at the first and third trimesters.
```{r}
data <- data %>% # remove indicator variables for the genes (duplicates)
  select(-c(mthfr677_pp, mthfr677_pq, mthfr677_qq, mthfr1298_pp, mthfr1298_pq, mthfr1298_qq, 
            mtrr_pp, mtrr_pq, mtrr_qq, tcn2_pp, tcn2_pq, tcn2_qq))

data <- data %>% # remove variables that are duplicates of variables that will be used in the analysis
  select(-c(subject.id, lbw2, live.birth2, num.babies3,
            couple3, edu8, income12, living.status5, married7, married2, mom.age3, mom.age5,
            smoker4, site11, 
            fol_quest2, fol.intake2, fol.intake4,
            fol.intake, tot_fol.t1, tot_fol.t3))

data <- data %>% # remove below LOD flags (not needed for analysis)
  select(-c(umfa.t1.flag:mefox.t1.flag)) %>% 
  select(-c(umfa.t3.flag:mefox.t3.flag)) %>% 
  select(-c(arsenic.t1.flag, cadmium.t1.flag, lead.t1.flag, manganese.t1.flag, mercury.t1.flag,
            arsenic.t3.flag, cadmium.t3.flag, lead.t3.flag, manganese.t3.flag, mercury.t3.flag))

# remove remaining variables that were never considered for the analysis
data <- data %>% 
  select(-c(high_bp:gerd)) %>% 
  select(-c(arsenic.t4.flag:mercury.t4.res))

data <- data %>% # remove non-methylated folate vitamer concentrations 
  select(-c(five_fTHF.t1.res, thf.t1.res, five_10_mnTHF.t1.res, mefox.t1.res,
            five_fTHF.t3.res, thf.t3.res, five_10_mnTHF.t3.res, mefox.t3.res))

data <- data %>% # remove variables that are not good candidates for being an auxiliary variable
  select(-c(birth.length, birth.wt, gest.age, lga2, sga2, 
            race.aboriginal2, race.asian2, race.black2, race.latin2, race.other2,
            mthfr1298_cat, mtrr_cat, tcn2_cat,
            manganese.t1.res, manganese.t3.res))

data <- data %>% # remove duplicates of the auxiliary variables
  select(-c(obese2, prepreg.bmi4, mom.birthplace2, alc))

```


## Move useful vars to the front
```{r}
# data <- data %>% 
#   select(c(srs,
#            lead.t1.res, lead.t3.res, 
#            sex2, 
#            fol.intake3, 
#            pl_fol3.t1, pl_fol3.t3,
#            mthfr677_cat, 
#            mthfr677_dom, mthfr677_rec,
#            pl_fol2.t1, pl_fol2.t3,
#            everything()))

data <- data %>% 
  select(c(lead.t1.res, lead.t3.res, 
           sex2, 
           fol.intake3, 
           pl_fol3.t1, pl_fol3.t3,
           mthfr677_cat, 
           mthfr677_dom, mthfr677_rec,
           srs, 
           everything()))
```

## log2 transform blood lead levels
```{r}
data <- data %>% 
  mutate(lead.t1.res = log2(lead.t1.res)) %>% 
  mutate(lead.t3.res = log2(lead.t3.res)) 
```


# implement MICE
```{r}
m <- 10

mice_data <- mice(data, m = m, printFlag = F, seed = 1010)
```




# analysis with standard interaction model

## prep
```{r}

list_level_names <- list(c("C|C", "C|T or T|T"),
                         c("C|C or C|T", "T|T"))
```


## Supplementary analysis
```{r}
# Dominant model (C|T and T|T together)

## t1
model_mice_int <- with(mice_data, lm(srs ~ lead.t1.res + mthfr677_dom + lead.t1.res:mthfr677_dom + sex2+ income4+ edu4+ living.status2+ home.score+ race.white2+ mom.age+ parity3+ city10+ year.enroll4 + smoker2 + srs.age))
table_int_supp <- get_mice_res_int(model_mice_int, name_z = "mthfr677_dom", name_x = "Lead, t1", 
                              level_names = list_level_names[[1]])

## t3
model_mice_int <- with(mice_data, lm(srs ~ lead.t3.res + mthfr677_dom + lead.t3.res:mthfr677_dom + sex2+ income4+ edu4+ living.status2+ home.score+ race.white2+ mom.age+ parity3+ city10+ year.enroll4 + smoker2 + srs.age))
table_tmp <- get_mice_res_int(model_mice_int, name_z = "mthfr677_dom", name_x = "Lead, t3", 
                              level_names = list_level_names[[1]])
table_int_supp <- rbind(table_int_supp, table_tmp)


# Recessive model (C|C and C|T together)

## t1
model_mice_int <- with(mice_data, lm(srs ~ lead.t1.res + mthfr677_rec + lead.t1.res:mthfr677_rec + sex2+ income4+ edu4+ living.status2+ home.score+ race.white2+ mom.age+ parity3+ city10+ year.enroll4 + smoker2 + srs.age))
table_tmp <- get_mice_res_int(model_mice_int, name_z = "mthfr677_rec", name_x = "Lead, t1", 
                                   level_names = list_level_names[[2]])
table_int_supp <- rbind(table_int_supp, table_tmp)

## t3
model_mice_int <- with(mice_data, lm(srs ~ lead.t3.res + mthfr677_rec + lead.t3.res:mthfr677_rec + sex2+ income4+ edu4+ living.status2+ home.score+ race.white2+ mom.age+ parity3+ city10+ year.enroll4 + smoker2 + srs.age))
table_tmp <- get_mice_res_int(model_mice_int, name_z = "mthfr677_rec", name_x = "Lead, t3", 
                              level_names = list_level_names[[2]])
table_int_supp <- rbind(table_int_supp, table_tmp)
```

# 3 way interaction
```{r}
# prep
level_names_fol <- c("≥20ᵗʰ percentile", "<20ᵗʰ percentile")
level_names_gene <- c("C|C", "C|T", "T|T")
level_names_gene_dom <- c("C|C", "C|T or T|T")
level_names_gene_rec <- c("C|C or C|T", "T|T")
```

## Main analysis 
MTHFR is a categorical variable with 3 levels
```{r}
# t1
model_mice_3 <- with(mice_data, lm(srs ~ lead.t1.res * pl_fol2.t1* mthfr677_cat + sex2+ income4+ edu4+ living.status2+ home.score+ race.white2+ mom.age+ parity3+ city10+ year.enroll4 + smoker2 + srs.age))

res_3way.t1 <- get_mice_res_3wayint_2z3w(model_mice_3, round = 1, name_x = "lead, t1", 
                                  name_z = "Plasma total folate conc., t1", name_w = "mthfr677_cat",
                                  level_names_z = level_names_fol, level_names_w = level_names_gene)

# t3
model_mice_3 <- with(mice_data, lm(srs ~ lead.t3.res * pl_fol2.t3* mthfr677_cat + sex2+ income4+ edu4+ living.status2+ home.score+ race.white2+ mom.age+ parity3+ city10+ year.enroll4 + smoker2 + srs.age))

res_3way.t3 <- get_mice_res_3wayint_2z3w(model_mice_3, round = 1, name_x = "lead, t3", 
                                  name_z = "Plasma total folate conc., t3", name_w = "mthfr677_cat",
                                  level_names_z = level_names_fol, level_names_w = level_names_gene)

table_3way <- rbind(res_3way.t1, res_3way.t3)

```

## Dominant assumption
```{r}
# t1
model_mice_3 <- with(mice_data, lm(srs ~ lead.t1.res * pl_fol2.t1* mthfr677_dom + sex2+ income4+ edu4+ living.status2+ home.score+ race.white2+ mom.age+ parity3+ city10+ year.enroll4 + smoker2 + srs.age))

res_3way.t1 <- get_mice_res_3wayint_2z2w(model_mice_3, round = 1, name_x = "lead, t1", 
                                  name_z = "Plasma total folate conc., t1", name_w = "mthfr677_dom",
                                  level_names_z = level_names_fol, level_names_w = level_names_gene_dom)

# t3
model_mice_3 <- with(mice_data, lm(srs ~ lead.t3.res * pl_fol2.t3* mthfr677_dom + sex2+ income4+ edu4+ living.status2+ home.score+ race.white2+ mom.age+ parity3+ city10+ year.enroll4 + smoker2 + srs.age))

res_3way.t3 <- get_mice_res_3wayint_2z2w(model_mice_3, round = 1, name_x = "lead, t3", 
                                  name_z = "Plasma total folate conc., t3", name_w = "mthfr677_dom",
                                  level_names_z = level_names_fol, level_names_w = level_names_gene_dom)

table_3way_dom <- rbind(res_3way.t1, res_3way.t3)
```

## Recessive assumption
```{r}
# t1
model_mice_3 <- with(mice_data, lm(srs ~ lead.t1.res * pl_fol2.t1* mthfr677_rec + sex2+ income4+ edu4+ living.status2+ home.score+ race.white2+ mom.age+ parity3+ city10+ year.enroll4 + smoker2 + srs.age))

res_3way.t1 <- get_mice_res_3wayint_2z2w(model_mice_3, round = 1, name_x = "lead, t1", 
                                         name_z = "Plasma total folate conc., t1", name_w = "mthfr677_rec",
                                         level_names_z = level_names_fol, level_names_w = level_names_gene_rec)

# t3
model_mice_3 <- with(mice_data, lm(srs ~ lead.t3.res * pl_fol2.t3* mthfr677_rec + sex2+ income4+ edu4+ living.status2+ home.score+ race.white2+ mom.age+ parity3+ city10+ year.enroll4 + smoker2 + srs.age))

res_3way.t3 <- get_mice_res_3wayint_2z2w(model_mice_3, round = 1, name_x = "lead, t3", 
                                         name_z = "Plasma total folate conc., t3", name_w = "mthfr677_rec",
                                         level_names_z = level_names_fol, level_names_w = level_names_gene_rec)

table_3way_rec <- rbind(res_3way.t1, res_3way.t3)
```

```{r}
table_3way_dom_rec <- rbind(table_3way_dom, table_3way_rec)
```


# Save
```{r}
#save as a csv file
write.csv(table_3way, row.names = F, file = paste0("moderation_code/raw results/3way int", 
                                                  "_",  Sys.Date(), ".csv", sep = ""))

# Dominant and recessive models
write.csv(table_int_supp, row.names = F, 
          file = paste0("moderation_code/raw results/moderation results_dom_rec", 
                                                  "_",  Sys.Date(), ".csv", sep = ""))

write.csv(table_3way_dom_rec, 
          row.names = F, file = paste0("moderation_code/raw results/3way int_dom_rec", 
                                                  "_",  Sys.Date(), ".csv", sep = ""))

```


# Clean results

## Clean 3 way interaction: main analysis
```{r}
res_all_3way <- table_3way %>% 
  mutate(res = paste0(beta, 
                      " (", 
                     lb, 
                      ", " ,
                      ub, 
                      ")", sep = " " ) )%>% # combine beta, lb, ub
  mutate(p_int_v2 = pvalue_rounder_jama(p_int)) %>% # fix p-value formatting
  mutate(p_int_v2 = ifelse(is.na(p_int) == T, 
                           "-", # add a dash when no p_int value is recorded
                           p_int_v2))%>%  
  arrange(x_name) %>% 
  select(c(x_name, z_name, z_level, w_level, res, p_int_v2)) 



```

## Clean main results: dom/ rec
```{r}
res_int_supp <- table_int_supp %>% 
  mutate(res = paste0(format(beta, nsmall = 1), 
                      " (", 
                      format(lb, nsmall = 1), 
                      ", " ,
                      format(ub, nsmall = 1), 
                      ")" ) ) %>% # combine beta, lb, ub
  mutate(p_int_v2 = pvalue_rounder_jama(table_int_supp$p_int)) %>% # fix p-value formatting
  mutate(p_int_v2 = ifelse(is.na(p_int) == T, 
                           "-", # add a dash when no p_int value is recorded
                           p_int_v2)) %>%  
  arrange(x_name, z_name) %>%
  select(c(x_name, z_name, z_level, res, p_int_v2)) %>%
  mutate(z_level = paste0("   ", z_level))
  
```

## Clean 3 way interaction: dom/ rec
```{r}
res_all_3way_dom_rec <- table_3way_dom_rec %>% 
  mutate(res = paste0(beta, 
                      " (", 
                     lb, 
                      ", " ,
                      ub, 
                      ")", sep = " " ) )%>% # combine beta, lb, ub
  mutate(p_int_v2 = pvalue_rounder_jama(p_int)) %>% # fix p-value formatting
  mutate(p_int_v2 = ifelse(is.na(p_int) == T, 
                           "-", # add a dash when no p_int value is recorded
                           p_int_v2))%>%  
  arrange(x_name) %>% 
  select(c(x_name, z_name, w_name, z_level, w_level, res, p_int_v2)) 
```

# save cleaned results
```{r}
#save as a MS excel file

write_xlsx(res_all_3way, path = paste0("moderation_code/results/res_3way int", "_",  Sys.Date(), ".xlsx", sep = ""))

write_xlsx(res_int_supp, path = paste0("moderation_code/results/res_int_supp", "_",  Sys.Date(), ".xlsx", sep = ""))

write_xlsx(res_all_3way_dom_rec, path = paste0("moderation_code/results/res_all_3way_dom_rec", "_",  Sys.Date(), ".xlsx", sep = ""))
```


```{r}

```




