---
title: "folate interaction with splines"
author: "Josh Alampi"
date: "2022-12-13"
output: html_document
---
# load
```{r}
#clear workspace
rm(list=ls(all=TRUE))

#load packages
library(readr); library(writexl) # for read_csv(); write_xlsx()  
library(plyr) # mapvalues()
library(MASS)
library(dplyr)
library(tidyr) # for gather()
library(ggplot2)
library(ggrepel); library(ggpubr); library(scales) # extra ggplot features
library(signs) # for signs_format(), uses proper minus sign instead of hyphen
library(lmtest) # for bptest()
library(quantreg)
library(bayesQR)
select <- dplyr::select
# library(rstan)
# library(emg) # for exponentially modified gaussian model

library(interactionRCS)
library(rms)

data <- read.csv("//ais-fs1.sfu.ca/home2/Redirected_Profiles/jalampi/Desktop/MIREC loader 2022/clean data/2023-10-04_MIREC data.csv")
```
https://raw.githack.com/gmelloni/interactionRCS/main/inst/extdata/vignette.html

# clean data

## make new variable: srs2
```{r}
data <- data %>% 
  mutate(srs2 = ifelse(srs >= 60, 1, 0))

table(data$srs2) # 11 with SRS score >= 60

```


## Eliminate participants with incomplete information
```{r}
data <- data %>% 
  filter(is.na(srs)==F) 

table(data$fol.intake3) 

data <- data %>% 
  filter(is.na(edu4)==F) %>% 
  filter(is.na(income4)==F) %>% 
  filter(is.na(home.score)==F)

table(data$srs2) 


```

## Clean
### Define reference level in confounders
The level that is the most common will be the reference level
```{r}
data$city10 <- factor(data$city10, levels = c(9,1,2,3,4,5,6,7,8,10)) # Montreal is Reference
data$edu4 <- factor(data$edu4, levels = c(3,1,2,4)) # undergrad is reference
data$income4 <- factor(data$income4, levels= c(4,1,2,3)) # >100K is reference
# data$mom.age3 <- factor(data$mom.age3, levels= c(2,1,3)) # 30-39 years old is reference # CUT
data$parity3 <- factor(data$parity3, levels= c(1,2,3)) #nulliparous is reference

data <- mutate(data, year.enroll4 = year.enroll4 - 2007)
data$year.enroll4 <- factor(data$year.enroll4, levels = c(3, 1, 2, 4)) # 2010 is reference

```

### make mean = zero for the cnts confounding variables
```{r}
data <- mutate(data, home.score = home.score - mean(home.score, na.rm = T))
data <- mutate(data, srs.age = srs.age - mean(srs.age, na.rm = T))
data <- mutate(data, mom.age = mom.age - mean(mom.age))
```

## Make t1, t3 datasets
```{r}
data.t1 <- data %>% 
  filter(is.na(lead.t1.res) == F) 

data.t3 <- data %>% 
  filter(is.na(lead.t3.res) == F)

```

## log transform exposure
```{r}
data.t1 <- data.t1 %>% 
  mutate(log2_lead.t1 = log2(lead.t1.res))

data.t3 <- data.t3 %>% 
  mutate(log2_lead.t3 = log2(lead.t3.res))
```

# analysis

## prep
```{r}
num_boot <- 1000
```

## t1 
### flexible model
```{r}
z_range <- c(quantile(data.t1$tot_fol.t1, 0.05, na.rm = T) : quantile(data.t1$tot_fol.t1, 0.95, na.rm = T))

# specify model
model.t1 <- glm(srs ~  log2_lead.t1 * rcs(tot_fol.t1, 3) + sex2+ income4+ edu4+ living.status2+ home.score+ race.white2+ mom.age + parity3+ city10+ year.enroll4 + smoker2 + srs.age, 
             data = data.t1, family = "gaussian")

# estimate the x-y associations for range of z
lr_rcs_boot.t1 <- intEST(model = model.t1, data = data.t1, var1 = "log2_lead.t1", var2 = "tot_fol.t1", 
                         var2values = z_range, ci.method = "bootstrap", R = num_boot)

# fig_rcs.t1 <- plotINT(lr_rcs_boot.t1, xlab = "Plasma Total Folate Concentrations (nmol/L)", line1 = F,
#                       ylab = "β") # make plot using interactionRCS package. Will make my own with ggplot instead. 
```

## t3 
### flexible model
```{r}
z_range <- c(quantile(data.t3$tot_fol.t3, 0.05, na.rm = T) : quantile(data.t3$tot_fol.t3, 0.95, na.rm = T))

# specify model
model.t3 <- glm(srs ~  log2_lead.t3 * rcs(tot_fol.t3, 3) + sex2+ income4+ edu4+ living.status2+ home.score+ race.white2+ mom.age + parity3+ city10+ year.enroll4 + smoker2 + srs.age, 
                data = data.t3, family = "gaussian")

# estimate the x-y associations for range of z

lr_rcs_boot.t3 <- intEST(model = model.t3, data = data.t3, var1 = "log2_lead.t3", var2 = "tot_fol.t3", 
                         var2values = z_range, ci.method = "bootstrap", R = num_boot)

# fig_rcs.t3 <- plotINT(lr_rcs_boot.t3, xlab = "Plasma Total Folate Concentrations (nmol/L)", line1 = F,
#                       ylab = "β") # make plot using interactionRCS package. Will make my own with ggplot instead. 
```

# make fig
## merge dataframes
```{r}
lr_rcs_boot.t1 <- lr_rcs_boot.t1 %>% 
  mutate(time = 1)

lr_rcs_boot.t3 <- lr_rcs_boot.t3 %>% 
  mutate(time = 3)

```

## fix labels
```{r}
lr_rcs_boot.t1 <- lr_rcs_boot.t1 %>% 
  mutate(time = "First trimester blood-lead levels (BLLs) and plasma \ntotal folate concentrations")

lr_rcs_boot.t3 <- lr_rcs_boot.t3 %>% 
  mutate(time = "Third trimester blood-lead levels (BLLs) and plasma \ntotal folate concentrations")

results_rcs <- rbind(lr_rcs_boot.t1, lr_rcs_boot.t3)
```


## Make figure
```{r}
text_size_minor <- 8
text_size_major <- 9
text_family <- "sans"

fig_rcs <- results_rcs %>% 
  ggplot() +
  geom_line(aes(x = Value, y = LIN)) + 
  geom_line(aes(x = Value, y = CI_L), colour = "grey", linetype = "dashed") + 
  geom_line(aes(x = Value, y = CI_U), colour = "grey", linetype = "dashed") + 
  geom_hline(yintercept = 0, lty = "dotted", size = 0.5) +
  facet_wrap(~time, scales = "free") +
  theme_bw() +
  labs(y = "β (Difference in SRS per 2-fold difference in BLLs)", x = "Plasma total folate concentrations (nmol/L)") +
  theme(text = element_text(family = text_family, colour = "black", size = text_size_minor)) +
  theme(axis.text = element_text(size=text_size_minor, colour = "black")) +
  theme(axis.ticks = element_line(size = 0.5, colour = "black")) + 
  
  theme(axis.title = element_text(size=text_size_major, colour = "black")) + 
  theme(strip.text = element_text(size=text_size_major, colour = "black"))  
  
fig_rcs
ggsave(file = paste0("moderation_code/results/fig_rcs", "_",  Sys.Date(), ".png"), width = 7, height = 3, dpi = 300)
ggsave(file = paste0("moderation_code/results/Figure 1.pdf"), width = 7, height = 3, dpi = 300)

```

## save raw results (for other to reproduce this figure) 
```{r}
write.csv(results_rcs, row.names = F, file = paste0("moderation_code/raw results/moderation results_RCS", "_",  Sys.Date(), ".csv", sep = ""))
```

## save cleaned up results for supplemental excel file
Will manually copy-paste this into an excel file, and finish cleaning up the title and labels there. 
```{r}
t1_results <- lr_rcs_boot.t1 %>% 
  mutate(Value = round(Value, 0)) %>% 
  mutate(LIN =   round(LIN, 1)) %>% 
  mutate(CI_L =  round(CI_L, 1)) %>% 
  mutate(CI_U =  round(CI_U, 1)) %>% 
  mutate(results = paste0(format(LIN, nsmall = 1), 
                      " (", 
                      format(CI_L, nsmall = 1), 
                      ", " ,
                      format(CI_U, nsmall = 1), 
                      ")" ) ) %>%
  select(c("Value", "results")) %>% 
  rename("Plasma total folate concentration" = "Value")  

t3_results <- lr_rcs_boot.t3 %>% 
  mutate(Value = round(Value, 0)) %>% 
  mutate(LIN =   round(LIN, 1)) %>% 
  mutate(CI_L =  round(CI_L, 1)) %>% 
  mutate(CI_U =  round(CI_U, 1)) %>% 
  mutate(results = paste0(format(LIN, nsmall = 1), 
                      " (", 
                      format(CI_L, nsmall = 1), 
                      ", " ,
                      format(CI_U, nsmall = 1), 
                      ")" ) ) %>%
  select(c("Value", "results")) %>% 
  rename("Plasma total folate concentration" = "Value")
```

```{r}
#save as a MS excel file
write_xlsx(t1_results, path = paste0("moderation_code/results/spline model results_t1", "_",  Sys.Date(), ".xlsx", sep = ""))
write_xlsx(t3_results, path = paste0("moderation_code/results/spline model results_t3", "_",  Sys.Date(), ".xlsx", sep = ""))
```

```{r}

```

